---
title: "Overview of YFAR functions"
date: "`r Sys.Date()`"
output:
  github_document:
    # toc: true
vignette: >
  %\VignetteIndexEntry{Overview of YFAR functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

*WooHoo!, finally an R package to get fantasy data from Yahoo!*

> **Before begining**
>
> This vignette assumes user has created and registered an app with the YDN
>

```{r, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup, message=FALSE, include = FALSE}
library(YFAR)
library(dplyr)
library(usethis)
devtools::load_all()
```

## INTRODUCTION

This is intended to be read like the opening crawl from Star Wars.

In a world dominated by python where no R tools existed for getting fantasy sports data out of the Yahoo! API.  A world where Googling "Yahoo fantasy sports R" or "yahoo in R" or "please not more python stuff, just an R package for getting fantasy data from yahoo" would just return more python libraries.  But not anymore!  If you Google "yahoo fantasy R", scroll down to more results, and then more results and probably more results a couple more times.... At last!  DAAA DAAA:

**YFAR - Yahoo Fantasy API w R**

A collection of functions that help you, help yourself to public fantasy data as well the data from past or present private leagues.  Even the ones where you finished second last, just ahead of someone who quit the draft after the first round and never logged in again.  Hey some years you just don't got it.  We've all been there.

A few notes for the user...

### Terminology.

I really try to use consistent language and labeling throoughout this project but please don't hold me to it.  This is on account of the fact that I was deep into this and them someone gave me a "good idea" and I essentially started all over again.  Now this project has really dragged on and now my mind is mush.

I will be referring to games or leagues and they are kinda synonymous but not really.  A game in this context is the fantasy sport you are playing or getting data for.  I.E. 2021 fantasy hockey is a game.

The overall structure is Game>League>Team>Roster>Players
 
This can be read as a game is made up of leagues, leagues are made up of teams, teams are made up of a roster, a roster is made up of players.

So while all players exist in the context of a game, they might not all exist in terms of a league.  If your league doesn't use goalies or defense these players will not exist in your league.

### A disclaimer.
There are a lot of disclaimers in this package.  This package was designed with hockey in mind but I tried to write the functions in a way that will accommodate all leagues.

### Tidyverse.
This package is written mostly with the tidyverse.  Maybe that was a mistake.

### Key nomenclature.
As you may notice the first argument of nearly all the functions is a key.  Sometimes it's key, sometimes it league_key. Why is that?  When a function accepts multiple types of keys the first argument is called key.  If a function only accepts one type of key then the first argument is explicit.

- Game key ex - 411
- League key ex - 411.l.1239
- Team key ex- 411.l.1239.t.1
- Player key ex - 411.p.6369

### Basic function heirarchy.
  - At its core YFAR has 3 types of functions:
    1. **Authentication**
    2. **Accessory Functions** 
    - Uninteresting but useful.  Mostly for acquiring data to supply as arguments to other functions i.e. weeks,            dates, team and league keys, etc.
    3. **The Beef**  
      - Probably why you are here.  Rosters, stats, standings, matchups etc.

### Function feedback and debugging.    
Each function is equipped with a `debug` argument and a `quiet` argument.

  - `quiet` is fairly self explanatory and allows toggling of function feedback messages.
  - `debug` allows the user to switch the return from a tibble to a list.  
  - If a function fails it will almost certainly be due to parsing.  The debug list return will contain:
    -  The response object.
    -  The response content.
    -  URI/s called.
    -  The resource.

This debug return will allow the user to still use the data or possibly parse the content oneself.

The debug return will be returned by tryCatch if the function fails.

### Memoisation.
In an attempt to speed things up and take pity on the API some of the functions are memoised.


## Getting started.
I registered an app at YDN and have my key and secret.  What now?  How do I start using this package?

- There are two core functions you will need to run to get started:
  1. `y_create_token()`
  2. `y_games()`
  
### Create a token.
The absolute first this you must do is create a token.  Every function has the `token_name` argument and the functions won't do function stuff without a token.
  
    y_create_token(my_key = NULL, my_secret = NULL, app_name = NULL)
    
A token is created using the **KEY** and **SECRET** given to you by the YDN as well as an app name. 
  
#### `y_create_token()`

    my_token <- y_create_token(my_key = "KEY", my_secret = "SECRET", app_name = "my_scraper")

Done and done but what exactly happened?

- This will create :
  - Token2.0 object.
  - Creates a file `.httr-oauth` which allows token refreshing.
  - If using version control will add `.httr-oauth` to `.gitignore`.

The token has some features which can help if you are getting http errors, specifically http error 401.

- Some of these include:
  - `my_token$can_refresh()` - check if token is refreshable
  - `my_token$refresh()` - refresh token

After creating a token you should not need to run `y_create_token()` again for the session.  You can just keep refreshing your existing token.  I've never actually timed how long between token refresh calls but it's around 20 minutes.

Now whenever you call a function you supply this value to the argument `token_name`.

## ACCESSORY FUNCTIONS
Next it a good idea to call some of the smaller accessory functions.  The returns from these functions are not all that interesting but will be used as inputs for the functions that probably brought you here.

### Get game info.
Now you can retrieve the general data from all the games you have participated in or are currently participating in.

#### `y_games()`
Here's where you get to use your token for the first time.

Let's check out your games.

    games <- y_games(token_name = NULL)

**The league_key and league_id are what will be used to tell the functions from which leagues you want data**

> Disclaimer
>
> For the examples here-on-in I'll use the league_key of a Yahoo! Public Fantasy Hockey League.
>
> 411.l.1239
>

OK enough with all this setup stuff.  Where the data at?

### Get week info.
The fantasy weeks corresponding to specific dates are handy to have.

    weeks <- y_weeks(game_key = NULL, token_name = NULL, debug = FALSE, quiet = TRUE)

#### `y_weeks()`
Use `y_weeks()` to get the match-up schedule for a game.  Here only the game key is necessary because the schedule for a game is set across all leagues.  All that changes is what week the league commences and the week playoffs start.

411 denotes 2021 Hockey

    weeks <- y_weeks(game_key = 411, token_name = my_token)

Well that return from `y_weeks()` wasn't exactly what I was hoping for.

I know right? Like I mentioned above we need to call some smaller functions to get the inputs for the functions that do the heavy lifting.

### Get team info.
Many functions take team keys as arguments so you should go ahead and grab some, especially for you teams.

#### `y_teams()`
Retrieve team data for teams in your league.  It may be handy to run this function upfront as it will return a column named `team_key` which can be used to get data for specific teams.

    y_teams(league_key = "411.l.1239", token_name = my_token)


> Disclaimer
>
> Most functions will accept a vector of keys.
>

## THE BEEF!
Now can get into the functions that probably brought you here.  Team stats, rosters, player stats, standings info and more.

### Get league info.

#### `y_league_settings()`
Retrieving the settings for a league will return nested tibbles of values pertaining to league settings, roster positions as well as other league information.

    y_league_settings(league_key = "411.l.1239", my_token, debug = FALSE, quiet = TRUE)
    
Extract an element to view the tibble.

    stat_cats <-league_settings$stat_categories

### Get team data.

#### `y_team_stats()`
Let's see some team stats.  I want to know how many goals my team has scored.

Accepts a league or team key. 

    team_stats_current_week <- y_team_stats(key = "411.l.1239", my_token)

The week param pertains to a particular week of the fantasy season.

- Accepts 3 arguments:
   - Default is `NULL` returns aggregated season stats.
   - `current` returns current week of season.
   - An integer corresponding to a week of season.
   
    `y_team_stats(key = "411.l.1239", my_token, week = NULL)`

Or select a week of season.

    y_team_stats(key = "411.l.1239", my_token, week = 5)

Or maybe you're only interested in your team.

    my_team_stats <- y_team_stats(key = "411.l.1239.t.1", my_token)

Or multiple teams.  Hey I'm not judging, been know to have 5 or 10 myself.

    my_team_stats <- y_team_stats(key = c("411.l.1239.t.1", "411.l.1239.t.2"), my_token)
    
#### `y_matchups()`
How do I see my matchups? Default arguments return past and current matchups

    my_matchups <- y_matchups("411.l.1239.t.1", my_token)

Also takes a week argument. Return week 8 matchup.

    my_week_8_matchup <- y_matchups("411.l.1239.t.1", my_token, week = 8)

##### Examples

Multiple weeks

    y_matchups(team_key = "411.l.1239.t.1", my_token, week = c(1, 8))

Multiple teams

    y_matchups(c(team_key = "411.l.1239.t.1", "411.l.1239.t.8"), my_token, week = 1)

Multiple teams with multiple weeks

    y_matchups(team_key = c("411.l.1239.t.1", "411.l.1239.t.8"), my_token, week = c(1, 8))

### Get transaction data.
I want to see all the moves made in my league this year. Can I do that? Yeah Baby!

> Disclaimer :
>
> Waiver claims are special transaction not covered by `y_transactions()`.
>

#### `y_transactions()`
Return all non-waiver transactions from a league.

     y_transactions(key = "411.l.1239", token_name = my_token, count = NULL, transaction_type = NULL, debug = FALSE, quiet = TRUE)

  - Arguments count and transaction_type can be supplied filter the return:
    - count :
      - a positive integer
    - transaction_type :
      - "commish"
      - "add"
      - "drop"
      - "trade"

##### Examples

Here are the last 5 transactions for team 1.  Notice that the length of the return will not necessarily be 5 because multiple players can be part of a transaction.

    y_transactions(key = "411.l.1239.t.1", token_name = my_token, count = 5)

The last 10 transactions in the league.

    y_transactions(key = "411.l.1239", token_name = my_token, count = 10)

The last trade in the league.

    y_transactions(key = "411.l.1239", token_name = my_token, count = 1, transaction_type = "trade")

Unfortunately as of right now you can't filter by date or sort with this function.

### Get player data.

These functions return meta data on players such as position eligibility, full name, jersey number etc.

#### `y_players()` vs `y_player_slate()`

> Disclaimer
>
> These functions don't return player stats.  Use `y_player_stats()` to retrieve player stats.
>

`y_players()` is intended to get a slice of players and takes arguments for specifying which and how many players to return.

The reason for this is that leagues contain a different number of players.  Due the Yahoo api only returning 25 players at a time a while loop is used to get the next 25 players until a response contains less than 25 players which is assumed to be the end of the resource.

Having said all that or TLDR use `y_player_slate()` to return all players that exist in your league.

#### `y_player_slate()`
Get all the players that exist in your league.  This function can be slow so it includes a progress bar.

> Disclaimer
>
> This function may be somewhat slow due to its use of janitor::make_clean_names.  I would/should change it but you don't love your dog as much as I love janitor.
>

league key

    y_player_slate(league_key = "411.l.1239", token_name = my_token)
    
game key

    y_player_slate(game_key = "411", token_name = my_token)
    
A game and league key may have different returns depending on sorting and filtering arguments. This is due to the fact that ranking depends on league settings.

#### `y_players()`
To get a slice of the players in your league.  By default starts at 0 and returns 100 players sorted by "AR" (actual rank).

    y_players("411.l.1239", token_name = my_token, start = 0, 
              number_of_players = 100, quiet = TRUE, debug = FALSE, ...)

Pass filters as key value pairs to ... arguments to customize your return.  The value should be a string i.e. status = "FA".

- Valid filters :
  - position (Valid player positions, e.g. position = "C")
  - status
    - All (all players)
    - A (all available players),
    - FA (free agents only),
    - W (waivers only),
    - T (all taken players),
    - K (keepers only)
  - search (player name e.g. /players;search=smith)
  - sort
    - {stat_id} (valid stat in your league e.g. sort by goals {/sort="1"}),
    - NAME (last, first),
    - OR (overall rank),
    - AR (actual rank),
    - PTS (fantasy points)
    - start (Any integer 0 or greater e.g. /players;start=25)
    - count (Any integer b/t 0 & 25 /players;count=5)

#### Examples.

Top 10 players filtered by all ownership types sorted by original (preseason) rank ("OR").

    y_players("411.l.1239", token_name = my_token, number_of_players = 10, sort = "OR", status = "ALL")

Top 10 players filtered by all ownership types and sorted by goals (stat="1").

    y_players("411.l.1239", token_name = my_token, number_of_players = 10, sort = "1", status = "ALL")

### Get draft results and ADP's.

I want to see the draft results from my league.  You must be able to that? Right you are! And average draft positions too?? ;)

#### `y_draft_results()`

League key:

    y_draft_results("411.l.1239", token_name = my_token, debug = FALSE, quiet = TRUE)

Or a team key:

    y_draft_results("411.l.1239.t.1", token_name = my_token, debug = FALSE, quiet = TRUE)


Who is player 411.p.2453? What is this mess?

The resource return from draft results is underwhelming as it doesn't include the player names or positions or anything intelligible.  Unless maybe you're Pierre Mcguire who surely has all these keys memorized.  But fear not....

Because the functions accept a vector of keys the player_key vector from draft_results can be used with `y_players()` or `y_rosters()`.

#### `y_draft_adp()`
I'm sure some viz enthusiasts will enjoy gettign their mitts on these numbers.  If given a game or league key the return will be eerily similar to `y_player_slate()` except it will have those 4 extra columns provided by the draft analysis sub-resource.  Ta Da!

Game key.
    `y_draft_adp(key = "411", token_name = my_token)`
    
League key.
    `y_draft_adp(key = "411.l.1239", token_name = my_token)`
    
Player key.
Last but not least probably the most succinct way to use `y_draft_adp()`, supply a vector of player keys. The player resource will contain the least amount of additional overhead information.

    y_draft_adp(key = vector_of_player_keys, token_name = my_token)

##### Examples

    unreadable_drafted_players <- y_draft_results("411.l.1239.t.1", token_name = my_token)
    
    my_player_keys <- unreadable_drafted_players$draft_result_player_key
    
    readable_drafted_players <- y_players(key = my_player_keys, token_name = my_token
    
See which players drafted by a team are still currently on the team's roster.

    dplyr::inner_join(
      y_rosters(key = "411.l.1239.t.1", my_token, debug = FALSE),
      y_draft_results(key = "411.l.1239.t.1", my_token, debug = FALSE),
      by = "player_key"
    ) %>% 
      dplyr::select("player_full")

### Get scoreboard data.
Is there a way to see all the league matchups?  YFAR says hold my beer and returns league wide matchup data.  Takes an integer week argument and the NULL default returns the current week.

#### `y_scoreboard()`

    y_scoreboard(league_key = "411.l.1239", token_name = my_token, week = NULL, debug = FALSE, quiet = TRUE)

An inevitable question :

Well what's the difference between y_matchups and y_scoreboard?  

They are similar and "under the hood" they use the same parsing functions but y_matchups takes a team key where y_scoreboard takes a league key.

In theory one could achieve the same return using y_matchups and mapping over the team_id's of a league but calling y_scoreboard is obviously easier.

So.....

##### Examples

Multiple leagues

    y_scoreboard(league_key = c(league_1_key, league_2_key), token_name = my_token)

Multiple weeks

    y_scoreboard(league_key = "411.l.1239", token_name = my_token, week = c(4, 5))
    
Both
    
    y_scoreboard(league_key = c(league_1_key, league_2_key), my_token, week = c(4, 5))
    
### Get standings data.
Wins, losses, win percentages, ya dig? Lets see some standings info!

#### `y_standings()`
Sad story,

This function is best use with `y_teams()` to supply a vector to team keys from a league.
It seems you should be able to supply a league key to this function but for some reason the request returns a bunch of team stats data and I wanted to keep that in the `y_team_stats()` function.

So lets start with one team.  This returns team and standings info.

    y_standings("41l.l.1239.t.1", my_token, debug = FALSE, quiet = TRUE)

##### Examples

All teams in your league

    teams_in_my_league <- y_teams(team_key = "411.l.1239", my_token)
    
    y_standings(team_key = teams_in_my_league, my_token)
    
### Get roster data.

If you are looking for the roster function here it is.  I put it at the bottle in a silly attempt to troll. I figure this is gonna be the most used function in the package but wanted to advertise the rest

#### `y_rosters()`

    y_rosters(key = NULL, token_name = NULL, game_date = NULL, debug = FALSE,                    quiet = TRUE)

##### Examples

League rosters

    y_rosters(key = "411.l.1239", token_name = my_token, game_date = NULL, debug = FALSE, quiet = TRUE)

Team Roster

    y_rosters(key = "411.l.1239.t.1", token_name = my_token, game_date = NULL, debug = FALSE, quiet = TRUE)

Date argument

A date argument can be supplied in the form YYYY-MM-DD.

    team_roster_w_date <- y_rosters(key = "411.l.1239.t.1", token_name = my_token, game_date = "2021-10-12")

Multiple dates

Create a date sequence from fantasy week 1 using return from `y_weeks()`.

    weeks <- y_weeks(game_key = 411, token_name = my_token)

    week_1 <- seq.Date(
                from = lubridate::ymd(weeks$start[1]), 
                to = lubridate::ymd(weeks$end[1]), 
                by = 1)

Use dates in `week_1` as `game_date` argument in `y_rosters`.

    y_rosters(key = "411.l.1239.t.1", token_name = my_token, game_date = week_1)

Multiple teams

    y_rosters(key = c(team_1, team_2), token_name = my_token, game_date = week_1)

Multiple Teams and Dates

    y_rosters(key = c(team_1, team_2), token_name = my_token, game_date = c("2021-12-01", "2021-12-02"))

### Get player stats.
The survey says this is the number 2 answer to "why are you here?".  Let's see some player stats! 
Unfortunately again this function is dependent on those pesky keys.  To get stats for players use a vector of player keys.

#### `y_player_stats()`

    y_player_stats(player_key = NULL, token_name = NULL, game_date = NULL, debug = FALSE, quiet = TRUE)
    
Here's a basic example using Leon Draisaitl.

    draisaitl_stats <- y_player_stats(player_key = "411.p.6369", token_name = my_token)

Well that's bs why can't I just use the player's name!? Where did you get that player key number anyways?

  - The player key can be found using:
      - `y_player_slate()`
      - `y_players()`
      - `y_rosters()`

#### Examples

Here's an example from the public league.

    y_rosters(id = "411.l.1239.t.1", token_name = my_token)

OK so what? I have to write down those numbers and run this function for each player?

Nope! `y_player_stats()` can take a vector of player keys.  Here's how using our roster from the last example.

    y_player_stats(player_key = team_1_roster$player_key, token_name = my_token)

OK well that's pretty good but what if I only want stats for my players from yesterday?

      y_player_stats(player_key = team_1_roster$player_key, token_name = my_token, 
                      game_date = Sys.Date() - 1)

And can it get my players stats for week 7?  Yes! You can supply a vector of dates.

Using y_weeks we can find the start and end date for week 7.

    weeks <- y_weeks(game_key = 411, token_name = my_token)

    week_7 <- 
      weeks %>%
      dplyr::filter(week == 7) %>%
      dplyr::select(start, end)

And create a date sequence

    week_7_dates <- 
      seq.Date(from = as.Date(week_7$start),
      to = as.Date(week_7$end),
      by = 1)

Week 7 player record count

    week_7_stats <-
      y_player_stats(
      players = team_1_roster$player_key,
      token_name = my_token,
      game_date = week_7_dates)
